---
title: <font color="#0241a3"> Warranty & Sentiment </font>
author: "Femi Adesanya"
date: "January 5 2018"
output: 
  html_document: 
    df_print: kable
    fig_height: 6
    fig_width: 9
    theme: united
    toc: yes
    toc_depth: 5
---


```{r, include = F}
package = c("qdap",      "tidyverse", "magrittr",   "knitr", 
            "markdown",  'quanteda',  "sentimentr", "igraph",
            "syuzhet",   "pracma",    "tidytext",   "stringr",  
            "readxl",    'ggraph',    "nlme",       "lubridate", 
            "wordcloud", "lexicon",   "plotly",     "textclean")

sapply(package, function(x) suppressMessages(require(x, character.only=T)))

opts_chunk$set(echo      = F, comment    = ">>>", warning   = F, 
               error     = F, cache      = F,     results   = "asis",
               message   = F, dpi        = 90,    fig.show  = "asis",  
               fig.align = "center")
```


```{r}
warranty = read_rds("C:/Users/26291/Documents/FEMI_FOLDER/data_all.rds") 

stop_words = 
  c(tm::stopwords("english"), lexicon::sw_python) %>% 
  tolower() %>% 
  unique()
```


```{r}
warranty_clean = 
  warranty %>%
  filter(!author %in% c("Chris", "John", "Mike")) %>%
  within(., {
    clean.rev = 
      review %>% 
      iconv("latin1", "UTF-8", sub = "") %>%
      replace_non_ascii() %>%
      replace_contraction() %>%
      replace_abbreviation() %>%
      replace_emoji() %>%
      replace_emoticon() %>%
      tolower() %>% 
      rm_url(replacement = " ") %>%
      rm_email(replacement = " ") %>%
      rm_stop(stopwords = stop_words, separate=F) %>%
      str_replace_all("\\b\\w{1,2}\\b", " ") %>% 
      str_replace_all("[\t\r\n]", " ") %>% 
      str_replace_all( 
     "[^\\!?.[:^punct:]]|[\\$]|\\=|\\>|\\<|\\~|\\`|\\^|\\+|\\|", " ") %>%
      str_replace_all("[[:digit:]]", " ") %>%
      rm_white() 
    clean.rev.stem = 
      clean.rev %>%
      stemmer(capitalize = F, char.keep = c(".", "?", "!"), warn = F)
  }) %>%
  mutate(nword = stringi::stri_count(clean.rev, regex = "[[:alpha:]]+"))
```


### <font color="tomato"> I. Textmining </font>


#### <font color="purple"> Word and document frequency based on tf-idf</font>



```{r}
tf_idf = 
  warranty_clean %>% 
  unnest_tokens(word, clean.rev.stem, token="words") %>% 
  count(brand, word, sort=T) %>%
  ungroup() %>%
  bind_tf_idf(word, brand, n) %>%
  arrange(desc(tf_idf))
```


```{r, fig.cap="Top 20 words based on tf-idf", fig.height=11}
p = 
  tf_idf %>%
  group_by(brand) %>%
  top_n(20, tf_idf) %>% # top ten words
  slice(1:20) %>%
  ungroup() %>%
  ggplot(aes(reorder(word, desc(tf_idf)), tf_idf, fill = brand)) +
  theme_classic() +
  geom_col(show.legend = FALSE, alpha = .5) +
  facet_wrap(~brand, ncol=1, scales="free") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
  labs(x="Terms", y="tf-idf")  +
  guides(fill=FALSE)
  
ggplotly(p, filename="legend/hiding")
```



#### <font color="purple"> Wordcloud of the most frequent words (top 100)</font>


```{r}
warranty_clean %>% 
  select(brand, clean.rev.stem) %>%
  corpus(text_field = "clean.rev.stem") %>%
  dfm(groups = "brand", verbose = F, 
      remove = "[[:punct:]]", valuetype = "regex") %>%
  dfm_weight(type = "tfidf") %>%
  textplot_wordcloud(comparison = T,  
                     colors = c("#f37736", "#7bc043", "#800080"), 
                     title.size = 1.5, 
                     scale = c(2.2, .7), 
                     max.words = 240, 
                     use.r.layout = T)
```



#### <font color="purple"> Identify multi-word expressions </font>


```{r}
colloc_data = NULL
n = 50
brd = warranty_clean$brand %>% unique()
for(i in seq_along(brd)) {
  tempo =
    warranty_clean %>%
    dplyr::filter(brand == as.character(brd[i])) %$%
    textstat_collocations(clean.rev.stem, size = 2, min_count=5) %>%
    top_n(n, desc(z)) %>%
    slice(1:n) %>%
    select(collocation, count) %>%
    mutate(brand = brd[i]) %>%
    separate(collocation, c("prefix", "suffix"), sep=" ") 
  colloc_data = rbind(colloc_data, tempo) %>% as.tibble()
}

```


```{r}
network = function(data, k){
  network = 
    data %>% 
    filter(brand == k) %>% 
    graph_from_data_frame() %>%
    ggraph(layout='igraph', algorithm='fr') +
    geom_edge_link(aes(edge_alpha = count, edge_width = count), 
                   edge_colour = "#40e0d0") +
    geom_node_point(size=2, colour="darkred") + 
    geom_node_text(aes(label=name), repel=T, point.padding=unit(0.1, "lines")) +
    theme_void() 
  return(network)
}
```

-- Company **Apple**

```{r, fig.width=11, fig.height=7}
network(colloc_data, brd[1])
```

-- Company **BestBuy**

```{r, fig.width=11, fig.height=7}
network(colloc_data, brd[2])
```

-- Company **Microsoft**

```{r, fig.width=11, fig.height=7}
network(colloc_data, brd[3])
```


### <font color="tomato"> II. Sentiment Analysis </font>


#### <font color="purple"> Sentiment distributions by company </font>


```{r, eval=T}
warranty_sent = 
  warranty_clean %>% 
  filter(nword > 2) %>% 
  mutate(score_sent = 
         sentiment_by(clean.rev, 
         polarity_dt = lexicon::hash_sentiment_senticnet,
         averaging.function=average_weighted_mixed_sentiment)$ave_sentiment) %>%
         cbind(., get_nrc_sentiment(.$clean.rev))
```


```{r}
#warranty_sent = readRDS("warranty_sent.rds")

warranty_sent %>% 
  filter(!is.na(score_sent)) %>%
  mutate(sentiment = ifelse(score_sent > 0.01, "Positive", 
                            ifelse(score_sent < -0.01, "Negative", NA))) %>%
  filter(!is.na(sentiment)) %>%
  group_by(brand) %>%
  dplyr::count(sentiment) %>%
  mutate(prop = n/sum(n)) %>%
  ungroup() %>%
  plot_ly(x      =~ brand, 
          y      =~ prop, 
          type   = 'bar', 
          color  =~ sentiment, 
          marker = list(line=list(color='black', width=1.5))) %>%
  layout(title = "", 
         xaxis = list(title = ""),
         yaxis = list(title = "Proportion"))
```


```{r}
library(qdap)
polarity = with(sentSplit(warranty_clean, "clean.rev"), 
               polarity(clean.rev, brand))

#polarity = readRDS("polarity.rds")
plot(scores(polarity)) 
```


#### <font color="purple"> Wordclouds by sentiment and company </font>



```{r}
cloud = function(data, tp, brd){
  cloud = lexicon::hash_sentiment_jockers_rinker %>% 
    rename(word=x, score_sent=y) 
  cloud = 
    inner_join(cloud, tf_idf, by="word") %>%
    select(brand, word, n, score_sent, tf_idf) %>%
    mutate(sentiment = ifelse(score_sent>0.01, "Positive", 
                            ifelse(score_sent<-0.01, "Negative", NA))) %>%
    filter(!is.na(sentiment)) %>%
    group_by(brand, sentiment) %>%
    top_n(tp, tf_idf) %>%
    slice(1:tp) %>%
    ungroup() %>%
    select(brand, word, sentiment, n) %>%
    arrange(brand, sentiment, n) %>%
    filter(brand == brd) %>% 
    select(-brand) %>%
    reshape2::acast(word ~ sentiment, value.var="n", fill=0)
  return(cloud)
  }
```

-- Company **Apple**

```{r}
cloud(tf_idf, 80, brd[1]) %>%
comparison.cloud(color = c("red", "green"), 
                 max.words = 100, 
                 title.size = 2, 
                 use.r.layout = T)
```

-- Comapny **BestBuy**

```{r}
cloud(tf_idf, 80, brd[2]) %>%
comparison.cloud(color = c("red", "green"), 
                 max.words = 100, 
                 title.size = 2, 
                 use.r.layout = T)
```

-- Company **Microsoft**

```{r}
cloud(tf_idf, 80, brd[3]) %>%
comparison.cloud(color = c("red", "green"), 
                 max.words = 100, 
                 title.size = 2, 
                 use.r.layout = T)
```


#### <font color="purple"> Emotions distributions by category </font>



```{r, fig.width=11}
warranty_sent %>% 
  dplyr::select(brand, anger:trust) %>%
  group_by(brand) %>%
  summarise(anger    = sum(anger, na.rm=T),
            anticipation = sum(anticipation, na.rm=T),
            disgust  = sum(disgust, na.rm=T),
            fear     = sum(fear, na.rm=T),
            joy      = sum(joy, na.rm=T),
            sadness  = sum(sadness, na.rm=T),
            surprise = sum(surprise, na.rm=T),
            trust    = sum(trust, na.rm=T)) %>%
  ungroup() %>%
  gather(emotions, freq, -brand) %>%
  group_by(brand) %>%
  mutate(prop = freq/sum(freq)) %>%
  ungroup() %>%
  plot_ly(x      =~ brand, 
          y      =~ prop, 
          type   = 'bar', 
          color  =~ emotions, 
          marker = list(line=list(color='black', width=1.5))) %>%
  layout(title = "",
         xaxis = list(title = " "),
         yaxis = list(title = "Proportion"))
```


### <font color="tomato"> III. Warranty association </font>


#### <font color="purple"> Association between warranty keywords and company </font>

```{r, fig.width=10}
keywords = dictionary(
  list(leave     = "leav*",   stay      = "stay*",
       buy       = "buy*",    not_buy   = "not buy*", 
       bad       = "bad*",    good      = "good*", 
       useful    = "usef*",   useless   = "usel*", 
       worth     = "wort*",   not_worth = "not wort*",
       expensive = "expens*", cheap     = "cheap*",
       happy     = "happ*",   unhappy   = "unhapp*",
       service   = "servic*")
  )
                  
dfm_relfreq = 
  warranty_clean %>%
  corpus(text_field = "clean.rev") %>%
  dfm(dictionary = keywords, remove_punct = TRUE, groups = "brand") %>%
  dfm_weight(type = "relfreq") %>%
  as.data.frame() %>%
  mutate(brand = rownames(.)) %>%
  gather(key = keywords, value = frequency ,-brand) %>%
  mutate(keywords = Hmisc::capitalize(keywords) %>% gsub("_", " ", .),
         frequency = round(frequency, 2))

p = 
  dfm_relfreq %>%
  ggplot(aes(x = reorder(keywords, frequency), y = frequency)) +
  geom_point(shape = 19, size = 3, color = "darkred", alpha = 0.3) +
  facet_wrap(~ brand, scales = "free") +
  coord_flip() +
  theme_classic() +
  labs(x = NULL, y = "Relative frequency")

ggplotly(p)
```


#### <font color="purple"> Association between synonymous and company </font>


```{r}
syno = list(
    leave = 
      c(synonyms("leave", F), "leave"),
    stay = 
      c(synonyms("stay", F), "stay"),
    buy = 
      c(synonyms("buy", F), "buy"),
    cheap = 
      c(synonyms("cheap", F), "cheap"),
    expensive = 
      c(synonyms("expensive", F), "expensive"),
    useful = 
      c(synonyms("useful", F), "useful"),
    useless = 
      c(synonyms("useless", F), "useless"),
    happy = 
      c(synonyms("happy", F), "happy"),
    unhappy = 
      c(synonyms("unhappy", F), "unhappy")
    ) %>% 
  dictionary()

dfm_syno = 
  warranty_clean %>%
  corpus(text_field = "clean.rev") %>%
  dfm(dictionary = syno, remove_punct = T, groups = "brand") %>%
  dfm_weight(type = "relfreq") %>%
  as.data.frame() %>%
  mutate(brand = rownames(.)) %>%
  gather(key = keywords, value = frequency ,-brand) %>%
  mutate(keywords = Hmisc::capitalize(keywords) %>% gsub("_", " ", .),
         frequency = round(frequency, 2))

p = 
  dfm_syno %>%
  ggplot(aes(x = reorder(keywords, frequency), y = frequency)) +
  geom_point(shape = 19, size = 3, color = "darkred", alpha = 0.3) +
  facet_wrap(~ brand, scales = "free") +
  coord_flip() +
  theme_classic() +
  labs(x = NULL, y = "Relative frequency")

ggplotly(p)
```



#### <font color="purple"> Locate keywords-in-context by company </font>


> Company Apple


```{r}
data_kwic1 = 
  warranty_clean %>%
  filter(brand == brd[1]) %$%
  kwic(tolower(review), keywords, 10, "glob") %>%
  as.tibble() %>%
  select(pre, keyword, post) %>%
  arrange(keyword) %>%
  DT::datatable(rownames = NULL, 
                colnames = c("Pre", "Keywords", "Post"),
                options = list(pageLength = 15, autoWidth = TRUE), 
                caption = "Keywords context in Apple reviews")

data_kwic1
```


> Company BestBuy


```{r}
data_kwic2 = 
  warranty_clean %>%
  filter(brand == brd[2]) %$%
  kwic(tolower(review), keywords, 10, "glob") %>%
  as.tibble() %>%
  select(pre, keyword, post) %>%
  arrange(keyword) %>%
  DT::datatable(rownames = NULL, 
                colnames = c("Pre", "Keywords", "Post"),
                options = list(pageLength = 15, autoWidth = TRUE), 
                caption = "Keywords context in BestBuy reviews")

data_kwic2
```



> Company Microsoft


```{r}
data_kwic3 = 
  warranty_clean %>%
  filter(brand == brd[3]) %$%
  kwic(tolower(review), keywords, 10, "glob") %>%
  as.tibble() %>%
  select(pre, keyword, post) %>%
  arrange(keyword) %>%
  DT::datatable(rownames = NULL, 
                colnames = c("Pre", "Keywords", "Post"),
                options = list(pageLength = 15, autoWidth = TRUE), 
                caption = "Keywords context in Microsoft reviews")

data_kwic3
```






